% -------------------------------------------------------------------------------------------------
%      MDSG Latex Framework
%      ============================================================================================
%      File:                  abstract.tex
%      Author(s):             Michael Duerr
%      Version:               1
%      Creation Date:         30. Mai 2010
%      Creation Date:         30. Mai 2010
%
%      Notes:                 - Place your abstract here
% -------------------------------------------------------------------------------------------------
%
\vspace*{2cm}

\begin{center}
    \textbf{Abstract}
\end{center}

\vspace*{1cm}

\noindent In recent years reinforcement learning(RL) showed substantial improvement in perfect information games such
as Chess or Go compared to traditional heuristic based approaches.
The aim of this study was to explore the capabilities of RL in games that do not feature perfect information.
As a case study we chose the bavarian card game Schafkopf, which is a 4 player trick game that features contract
bidding, including solo and team play. S
I outlined the implementation for Schafkopf using Python and range of Computer players that use varying strategies
for move Selection. Statistical analysis was then used to explore the domain.
Following were players implemened: Random Player, Heuristic, QLearining Player, Simulation Player, Improved
Simulation Player
Reinforcement learning was then applied to all game phases such as bidding and consequent move selection.
Computer strength was compared for a bootstrapping approach, using a collection of human games, versus as a zero
knowledge approach.
Furthermore a GUI allowed playing the Computer.